\documentclass{article}
\usepackage{synttree}
\usepackage{stmaryrd}
\usepackage{pbox}

\makeatletter
\newbox\MTr@alignbox
\newcommand\aligncenter[1]{%
  \setbox\MTr@alignbox=\hbox{#1}%
  \parbox{\wd\MTr@alignbox}{\unhbox\MTr@alignbox}}
\newcommand\aligntop[1]{%
  \setbox\MTr@alignbox=\hbox{#1}%
  \MTr@templength 1sp%
  \raisebox{-\the\MTr@treedepth\MTr@templength}{\unhbox\MTr@alignbox}}
\makeatother

\begin{document}
\childattachsep{0.6in} 
\childsidesep{0.9em}

\title{Synttree test cases}
\author{Matijs van Zuijlen}
\maketitle

\section{Basic}

These are test cases for synttree.

All cases are left-aligned. Their
leftmost border should be on the same vertical as the start of this
paragraph.

    \synttree[A[ A    ]] \hfill Single child, no label issues

    \synttree[ A [ AA ]] \hfill single child, bottom label is wider

    \synttree[AA[A]] \hfill single child, top label is wider

    \synttree[A[.t AA]] \hfill single child, triangle

    \synttree[A[ b a a    a a a b][D]] \hfill Spaces in label are
    handled like regular \TeX.

    \synttree[A[aa a a a a a aa [E][.t FFFFFFFF]][D[.t ZZ]]]
    \hfill with some triangles, slightly weird.

    \synttree[A[B][C][D]] \hfill three children

    \synttree[A[B][C][D][E]] \hfill four children

    \synttree[A[B][C][D][E][F][G][H][I][J][K][L][M]]
    
    \hfill 12 children

    \synttree[A[\shortstack{\strut B \\ \strut (C)}
      [D(E)]]] \hfill Big label

    \synttree{4} [A[B[E[F]][C]][D[.b Z]]]
    \hfill With a bottom node

\newpage

\section{Trees within other structures.}

Sometimes, trees can show up inside paragraphs (o, really?) or mathematical
formulas:

    Start\mbox{\synttree[A[ A ]]}End
    \hfill{Bottom lines up. May not be what we really want.}

  Inside \synttree [A[a][paragraph]].
  \hfill With downward-extending letters. Looks bad.

  $\left\llbracket\aligncenter{\synttree [A[B[E[F]][C]][D[Z]]]}\right\rrbracket$
    \hfill Big semantic brackets.

  $\left\llbracket 1+ \aligncenter{\synttree [A[B][C]]} - 3 \right\rrbracket$

\section{Faking maximum depth}

\synttree{4}[A [B [.b C]] [C [D[E[F]]]]]

\section{Special labels}

    \synttree[A[.t $\sum_0^5(25)$ ]] \hfill Equation

\section{Alignment}
Default is alignment at the bottom. Alignment at the center can go like
this:

Here is a paragraph with \aligncenter{\synttree[an [embedded] [tree]]}\ in
it. Let's make this paragraph a little longer to demonstrate what happens
with word wrapping.

Here is a paragraph with \aligntop{\synttree[an [embedded] [tree]]}\ in it,
top aligned. Let's make this paragraph a little longer to demonstrate what
happens with word wrapping.

Here is a paragraph with \synttree[an [embedded] [goody]] in
it, bottom aligned. Let's make this paragraph a little longer to
demonstrate what happens with word wrapping.

\end{document}
